\section{PROJECTS}

\textbf{Binance Trading Bot \hfill Feb 2020 - Present} \vspace{0.1cm} \\
    Personal Project. A leverage trading bot on Binance using Heikin Ashi calculations mainly focusing on Momentum and Swing strategies. The bot is deployed on GCP and running 24/7. \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Technology/Tools :} Binance API, Python, Quantiacs, GCP
        \item \textbf{Link to the Project :} \url{https://github.com/zyairelai/buy-low-sell-high}
    \end{itemize}

\textbf{Mind-Controlled Drone \hfill Jul - Aug 2020} \vspace{0.1cm} \\
    Self Project during Quarantine. Mounting the mindata chip from the existing Mind-Controlled Wheelchair (Check Below) onto the \$10 drone set that made in China \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Technology/Tools :} Arduino, Java, MultiWii
        \item \textbf{Link to the Drone :} \url{https://github.com/louiszhenyean/bci-drone/}
    \end{itemize}
    
\textbf{Zyummy: Food Recipe Website \hfill Apr - May 2020} \vspace{0.1cm} \\
    Self Project during Quarantine. A website meant to be ease my personal cooking recipe and random recipe found on the internet.  \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Technology/Tools :} HTML, CSS
        \item \textbf{Link to the Website :} \url{https://louiszhenyean.github.io/zyummy/}
    \end{itemize}

\textbf{Data Compression \& Data Hiding during Data Ingestion \hfill Aug - Nov 2019} \vspace{0.1cm} \\
    My Final Year Project. A Java based web application which compress data file and hide it over an audio file. The output file is an audio file which has no difference from the original audio file. With the specific decryptor, the hidden data in the audio file can be retrieved. \vspace{0.3cm}
    \begin{itemize}
        \item \textbf{Technology/Tools :} Java, TomCat, MySQL, Hadoop HDFS, HTML
        \item \textbf{Link for Encryptor :} \url{https://github.com/louiszhenyean/StegaSender}
        \item \textbf{Link for Decryptor :} \url{https://github.com/louiszhenyean/StegaRetriever}
    \end{itemize}

\textbf{Mind-Controlled Wheelchair \hfill Jul - Aug 2019} \vspace{0.1cm} \\
    Academic Technopreneurship Team Project. Worked in a 4 person team to develop a brain-computer interface wheelchair model controlled using EOG/EEG brain signals. The input is the brainwave signals read by Mindata chip and the movement of the wheelchair is determined by the different forms of brainwave signals. \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Technology/Tools :} Arduino, Python, OpenBCI
        \item \textbf{Link to our product Video Pitching :} \url{https://youtu.be/V-fi6DpGpFk}
        \item \textbf{Link for the Mindata Chip :} \url{http://www.mindatabci.com/en/}
    \end{itemize}
