\section{ACADEMIC PROJECTS}
\title{\textbf{Data Compression \& Data Hiding during Large Data Ingestion}}
\begin{position}
\end{position}
\vspace{-1.2cm}
\title{\textbf{Academic Project: Final Year Project \hfill August - Nov 2019}}
\begin{position}
    A Java based web application which compress data retrieved from MySQL database, then hide the data over an audio file. The output file is known as "stega-audio". The stega-audio is then forwarded to HDFS storage. The stega-audio file is simply an audio file which has no difference from the original audio file. With the specific decryptor, the hidden data in the audio file can be retrieved. \vspace{0.3cm}
    \begin{itemize}
        \item \textbf{Technology/Tools :} Java, TomCat, MySQL, Hadoop HDFS, HTML
        \item \textbf{Link for Encryptor :} \url{https://github.com/louiszhenyean/StegaSender}
        \item \textbf{Link for Decryptor :} \url{https://github.com/louiszhenyean/StegaRetriever}
    \end{itemize}
\end{position}

\textbf{Mind Controlled Wheelchair \hfill Jul - Aug 2019} \\
    Worked in a 4 person team to develop a brain-computer interface wheelchair model controlled using EOG/EEG brain signals in our Technopreneurship Team Project. The input is the brainwave signals read by Mindata chip and the movement of the wheelchair is determined by the different forms of brainwave signals. \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Technology/Tools :} MatLab, Arduino
        \item \textbf{Link for Mindata Chip :} \url{http://www.mindatabci.com/en/}
    \end{itemize}

\textbf{Face Recognition Attendance System \hfill Jul - Aug 2019} \\
    Worked in a 4 person team to develop a desktop based application in Python. The application provides an interface to compare the input photo of the students' face with the data-set photos. I was responsible for designing the structure related to the face recognition neural network and writing code in Python. \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Technology/Tools:} Python, OpenCV, pickle
    \end{itemize}

\textbf{Wireless Channel Control Hovercraft \hfill Feb - May 2018} \\ 
    Worked in a 4 person team to create a remote hovercraft using scrap materials like plastic bags, plastic bottles, polystyrene, and old toy cars. \vspace{0.2cm}

\textbf{Self-Signed Certificate Web Server \hfill Oct - Dec 2017} \\
    Deploy an Apache Web Server directory website with self-signed certificate. \vspace{0.2cm}

\textbf{Food Ordering System \hfill Jul - Aug 2017} \\
    Hardcore pure HTML \& CSS coding for food ordering website for the campus. \vspace{0.2cm}