\section{COMPETITIONS}
\par

\textbf{Brain-Computer Interface (BCI) Contest using \\ Mind-Controlled Drone \hfill Nov 2019} \\
    Worked in a 4 person team to develop a drone that is controlled using EEG brain signals. The drone set and the Mindata chips are sponsored by the company BrainTech. \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Link :} \url{https://bcitechcontest.com/competition-information/}
    \end{itemize}

\textbf{Ankara Capture the Flag (CTF) Contest \hfill Oct 2017} \\
    Capture the user flag and root flag by penetrating into a Virtual Operating System that is hosted by the competition unit. The fastest team gets the place. \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Link :} \url{https://www.stm.com.tr/en/news/announcement/stm-capture-the-flag-2017-turkeys-most-comprehensive-cyber-contest-draws-to-a-close}
    \end{itemize}

\textbf{GPU/CUDA Programming Competition \hfill Aug 2017} \\
    Worked in a 4 person team to write code in CUDA-C language for a program that analyze how many car park empty spaces are available after a video scan by the remote drone. The program must be running using Graphical Processor Unit. \vspace{0.2cm}

\textbf{The E-Genting Programming Competition \hfill Nov 2016} \\
    A competition that given real life situation and start writing code without a computer, however, books are allowed in the competition. \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Link :} \url{http://egpc.genting.com.my/Events.aspx}
    \end{itemize}

\textbf{The E-Genting Bug Hunt \hfill Nov 2016} \\
    A competition that finding bug from given code in paper without a computer. \\
    However, reference books are allowed in the competition. The output is a software test documentation. \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Link :} \url{http://egbh.rwgenting.com/Archive.aspx}
    \end{itemize}
